Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-29 papers/ms.tex
update ms
Adam Kraus comments round 1:

Add description of all the KOI matches.

Clarify Fig 3 upper

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new window
  on open cluster dispersal.  Here we present an analysis of a group
  stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

This unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBSCAN-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler.  An important
consideration, especially for CH-2, is the contamination rate by field
stars.  We assess this in the following section.

@@

The adopted stellar parameters are listed in
Table~\ref{tab:sysparams}.  The stellar surface gravity, radius, mass,
and density are found by interpolating against the MIST isochrones
\citep{choi_mesa_2016}.  The statistical uncertainties from this
technique mostly originate from the parallax uncertaintes; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is induced by starspots.  {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori transit model is shown with the gray line, and the
    residual after subtracting the transit model is vertially
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

The Kepler space telescope observed Kepler-1643, KOI-7913, and
KOI-7368 at a 30-minute cadence between May 2009 and April 2013.  For
all three systems quarters 1 through 17 were observed with minimal
data gaps.  The top panel of Figure~\ref{fig:planets} shows a 50-day
slice of the \texttt{PDCSAP} light curves for the three new Cep-Her
candidates, along with Kepler-1627.  In \texttt{PDCSAP},
nonastrophysical variability is removed through a cotrending approach
that uses a set of basis vectors derived by applying singular value
decomposition to a set of systematics-dominated light curves
\citep{smith_kepler_PDC_2017}.  In our analysis, we used the
\texttt{PDCSAP} light curves with the default optimal aperture
\citep{smith_finding_2016}.  Cadences with non-zero quality flags were
omitted.  In all cases, the stars are dominated by spot-induced
modulation with peak-to-peak variability between 2\% and 10\%.  These
signals are much larger than the transits, which have depth
$\approx$0.1\%.  To quantify the stellar rotation periods, we
calculated the Lomb-Scargle periodogram for each Kepler quarter
independently.  The resulting means and standard deviations are in
Table~\ref{tab:sysparams}.

@@

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 (omitting KOI-7913.01).  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discusssed ($\approx$$14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet is statistically validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate'' (see Appendix~\ref{app:koi7913}).  The most likely
explanation is the presence of KOI-7913~B, which is located
approximately one Kepler pixel away from Kepler-7913 A.  Our
pixel-level analysis of the target pixel files did not show any
evidence to support the idea that KOI-7913~B could host the transiting
planet.  Our NIRC2 imaging similarly ruled out the possibility of any
other plausible host star for the planet other than KOI-7913~A.

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr stellar assocation.  It would be a
worthy exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other Cep-Her groups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  An important
aspect of the remaining work will be to acquire radial velocities of a
large subset of the stars, to assess whether the traceback approach
could be applicable.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  If Gaia DR3 provides RVS spectra for the brighter F and G
dwarfs, these would also contain the calcium infrared triplet as
another age indicator.  These indicators, combined with better
kinematics, would help in definitively unravelling the formation
history of the complex.

@@

The astrophysical implicatoin of these considerations is that planets
$\approx$2 Earth radii in size exist at ages of 40 million years.  It
will be interesting to continue the push down to smaller planetary
sizes at comparable ages -- the planetary detections we have presented
are well above the average detection significance for Kepler planets.
There may still be room at the bottom.

@@

%\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

\appendix
\section{Tables of Candidate Cep-Her Members}
\label{app:members}

\paragraph{Table~2} contains candidate Cep-Her members with weights
$D>0.02$ observed by Kepler.  The final catalog of candidate
Cep-Her members will be provided by R.~Kerr et al.\ in prep.; Table~2 is
from a preliminary version of that same catalog.  Note that more
restrictive weight cuts should be imposed should one wish to remove
the majority of field star interlopers; at least half of the stars
included in the table are unlikely to be bonafide Cep-Her members.
Table~2  was created by cross-matching candidate Cep-Her members
(selected using Gaia EDR3; Section~\ref{subsec:members}) against a
Kepler to Gaia DR2 cross-match (the \texttt{gaia-kepler.fun}
crossmatch database created by Megan Bedell).  The
\texttt{kic\_dr2\_ang\_dist} column is from the latter table.  The
EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.

@@

\begin{figure*}[b]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new window
  on open cluster dispersal.  Here we present an analysis of a group
  of stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.  Kepler-1627 is in the outskirts of the $\delta$ Lyr
  cluster \citep{bouma_kep1627_2022}, which is centered at $(l,b)
  \approx (66^\circ, 12^\circ)$.
  The Kepler footprint is shown in gray.
  {\it Middle row}: Galactic positions.  The Sun is at $(X, Y, Z) =
  (0, 0, 20.8)$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for all of the stars displayed
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

This unsupervised clustering in this case yielded 8 distinct subgroups.
These groups are then used as the ``seed'' populations for the third
step, which is to search for objects at least as close to the 10$^{\rm
th}$ nearest HDBScan-identified member in space-velocity coordinates.
This third step yields stars that are spatially and kinematically
close to the photometrically young stars, but which cannot be
identified as young based on their positions in the color--absolute
magnitude diagram.

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater spatial extent toward smaller
$X$ (Figure~\ref{fig:XYZvtang}, middle panels).  For the diffuse stars
near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2'', using the preliminary 
Cep-Her (CH) subgroup identifier from R.~Kerr et al.\ (in prep).
These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler, and all of our
candidate matches against the Kepler Objects of Interest.  An important
consideration, especially for CH-2, is the contamination rate by field
stars.  We assess this in the following section.

@@

The adopted stellar parameters are listed in
Table~\ref{tab:sysparams}.  The stellar surface gravity, radius, mass,
and density are found by interpolating against the MIST isochrones
\citep{choi_mesa_2016}.  The statistical uncertainties from this
technique mostly originate from the parallax uncertainties; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}: 50 day light curve segment from the 3.9 years of Kepler
    data.  The ordinate shows the \texttt{PDCSAP} median-subtracted
    flux in units of parts-per-thousand ($\times 10^{-3}$).  The
    dominant signal is from starspots; planetary transit times
    are indicated but the individual transits are not visible at this scale.
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum a
    posteriori model is shown with the gray line, and the
    residual after subtracting the transit model is vertically
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

@@

The Kepler space telescope observed Kepler-1643, KOI-7913, and
KOI-7368 at a 30-minute cadence between May 2009 and April 2013.  For
all three systems quarters 1 through 17 were observed with minimal
data gaps.  The top panel of Figure~\ref{fig:planets} shows a 50-day
slice of the \texttt{PDCSAP} light curves for the three new Cep-Her
candidates, along with Kepler-1627.  In \texttt{PDCSAP},
non-astrophysical variability is removed through a cotrending approach
that uses a set of basis vectors derived by applying singular value
decomposition to a set of systematics-dominated light curves
\citep{smith_kepler_PDC_2017}.  In our analysis, we used the
\texttt{PDCSAP} light curves with the default optimal aperture
\citep{smith_finding_2016}.  Cadences with non-zero quality flags were
omitted.  In all cases, the stars are dominated by spot-induced
modulation with peak-to-peak variability between 2\% and 10\%.  These
signals are much larger than the transits, which have depth
$\approx$0.1\%.  To quantify the stellar rotation periods, we
calculated the Lomb-Scargle periodogram for each Kepler quarter
independently.  The resulting means and standard deviations are in
Table~\ref{tab:sysparams}.

@@

\paragraph{KOI-7913}
KOI-7913.01 is also currently listed on the NASA Exoplanet Archive as a
``candidate'' planet.  The \citet{morton_false_2016}
analysis was of Q1-Q17 KOIs from DR24, and therefore spanned KOI-1.01
to KOI-7620.01 (omitting KOI-7913.01).  However the results of the
subsequent DR25 analysis by Morton et al.\ are listed at the NASA
Exoplanet Archive.  The relevant table gives a probability for the
system being an astrophysical false positive of $1.4\times10^{-4}$,
with the most likely false positive scenario being a blended eclipsing
binary.  Repeating the calculation with our new detrending and
contrast curves, we find a similar result: ${\rm FPP} =
1.3\times10^{-4}$.  Though the transit has the lowest S/N of any of
the objects discussed ($\approx$$14$), its lower FPP relative to
KOI-7368 can be understood through its flat-bottomed shape,
combined with its long transit duration relative to plausible
eclipsing binary models (Figure~\ref{fig:planets}).  The host star
probability usability score \citep{2017ksci.rept...16B} also meets the
usual threshold, and so the planet is statistically validated.  Its
disposition has however previously fluctuated from ``false positive''
to ``candidate'' (see Appendix~\ref{app:koi7913}).  The most likely
explanation is the presence of KOI-7913~B, which is located
approximately one Kepler pixel away from Kepler-7913 A.  Our
pixel-level analysis of the target pixel files did not show any
evidence to support the idea that KOI-7913~B could host the transiting
planet.  Our NIRC2 imaging similarly ruled out the possibility of any
other plausible host star for the planet other than KOI-7913~A.

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr stellar association.  It would be a
worthy exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other Cep-Her groups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  An important
aspect of the remaining work will be to acquire radial velocities of a
large subset of the stars, to assess whether the traceback approach
could be applicable.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  If Gaia DR3 provides RVS spectra for the brighter F and G
dwarfs, these would also contain the calcium infrared triplet as
another age indicator.  These indicators, combined with better
kinematics, would help in definitively unraveling the formation
history of the complex.

@@

The astrophysical implication of these considerations is that planets
$\approx$2 Earth radii in size exist at ages of 40 million years.  It
will be interesting to continue the push down to smaller planetary
sizes at comparable ages -- the planetary detections we have presented
are well above the average detection significance for Kepler planets.
There may still be room at the bottom.

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

\appendix
\section{Candidate Cep-Her Members}
\label{app:members}

\paragraph{Table~2} contains candidate Cep-Her members with weights
$D>0.02$ observed by Kepler.  The final catalog of candidate
Cep-Her members will be provided by R.~Kerr et al.\ in prep; Table~2 is
from a preliminary version of that work.  Note that more
restrictive weight cuts should be imposed should one wish to remove
the majority of field star interlopers; at least half of the stars
included in the table are unlikely to be bonafide Cep-Her members.
Table~2  was created by cross-matching candidate Cep-Her members
(selected using Gaia EDR3; Section~\ref{subsec:members}) against a
Kepler to Gaia DR2 cross-match (the \texttt{gaia-kepler.fun}
crossmatch database created by Megan Bedell).  The
\texttt{kic\_dr2\_ang\_dist} column is from the latter table.  The
EDR3 to DR2 match was performed using the
\texttt{gaiaedr3.dr2\_neighbourhood} table, and the closest proper
motion and epoch-corrected angular distance neighbor was taken as the
single best match.  The \texttt{edr3\_dr2\_mag\_diff} column gives
some indication of the reliability of this EDR3 to DR2 conversion, as
there are a few cases between Gaia DR2 and EDR3 where partially
resolved binaries became fully resolved.

\paragraph{Candidate matches between Cep-Her and the Kepler Objects of
Interest:}
The full list of candidate matches between Cep-Her and the Kepler
objects of interest is as follows -- the objects are listed in order
of descending weights, $D$.
Objects designated as confirmed planets included
Kepler-1627,
Kepler-1643,
Kepler-1331,
Kepler-1062, and
Kepler-1933.  % Newly validated by Valizadegan+2022
Objects designated as candidate planets included
KOI-5264,
KOI-8007,
KOI-7572,
KOI-7375,
KOI-7368,
KOI-7638,
KOI-5632, and
KOI-7913.
Objects designated known false positive planet candidates included
KOI-6437, 
KOI-5988, 
KOI-7871,
KOI-7655,
KOI-5024,
KOI-61,
KOI-4336,
KOI-6812,
KOI-3399, and
KOI-6277.
Finally, Kepler-1902 (KOI-3090) has one confirmed planet
(KOI-3090.02), and one false positive (KOI-3090.01).
Of these objects, only Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913 met our requirements for potentially
both {\it i)} having real planets, and {\it ii)} being $\lesssim 10^8$
years old, based on the presence of rotational modulation at the
expected period and amplitude.  One object was ambiguous: Kepler-1933.
This system has a confirmed $\approx$$1.4\,R_\oplus$ planet, a stellar
rotation period of 6.5\ days, and an effective temperature of $\approx$$5750\,{\rm K}$.  This places it near the upper envelope of the
rotation period vs.\ color distribution for the Pleiades, making
it unlikely to be $\approx$40\,Myr old.  Nonetheless, we acquired a
reconnaissance HIRES spectrum, and it yielded ${\rm EW}_{\rm Li} = 93 \pm
5$\,m\AA.  Combined with the rotation period, this suggests an age
between 100 and 200\,Myr for Kepler-1933, but the system is
unlikely to be part of Cep-Her.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}
